A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-12-28 pilot-publication/lab-book.Rmd
Edit lab-book
Add code to generate outcome tables

@@

>>>>

## Import saved outcome results and create outcome tables

```{r}
## Load outcome results
outcome.results <- readRDS("outcome-results.rds")

## Extract cell references
cell.references <- names(outcome.results$point.estimates)

table.names <- strsplit(cell.references, split = "\\|\\|\\.") %>%
    lapply(function(table.name) table.name[1]) %>%
    unique()

ci.levels <- outcome.results$confidence.intervals[[2]][, 1]

## Combine point estimates and confidence intervals into a single table
combined.outcome.results <- lapply(ci.levels, function(ci.level) {
    lapply(cell.references, function(cell.reference) {
        point.estimate <- outcome.results$point.estimates[[cell.reference]]
        ci.data <- outcome.results$confidence.intervals[[cell.reference]]
        ci <- ci.data[ci.data[, 1] == ci.level, c("lower", "upper")]
        combined <- NA
        if (!all(is.na(ci))) {
            combined <- sprintf("%0.2f", c(point.estimate, ci))
            combined <- paste0(combined[1], " (", combined[2], ", ", combined[3], ")")
        }
        return(combined)
    }) %>%
        setNames(cell.references)
}) %>%
    setNames(paste0("ci.level.", ci.levels))

## Create outcome tables
create_ci_level_tables <- function(table.name, ci.data) {
    print(table.name)
    table.data <- ci.data[grep(table.name, names(ci.data), fixed = TRUE)]
    column.names <- strsplit(names(table.data), split = "\\|\\|\\.") %>%
        lapply(function(column) column[2]) %>%
        unique() %>%
        stringr::str_replace_all(pattern = "\\|\\|column\\:\\:", replacement = "")
    row.names <- strsplit(names(table.data), split = "\\|\\|\\.") %>%
        lapply(function(row) row[3]) %>%
        unique() %>%
        stringr::str_replace_all(pattern = "\\|\\|row\\:\\:index\\:[0-9]*\\:\\:", replacement = "") %>%
        stringr::str_replace_all(pattern = "\\|\\|", replacement = "")
    ci.table <- matrix(table.data, ncol = length(column.names)) %>%
        tibble::as_tibble(.name_repair = "minimal") %>%
        tibble::add_column(row.names, .before = 1, .name_repair = "minimal") %>%
        setNames(c("Outcome", column.names))
    return(ci.table)
}

tables <- lapply(
    combined.outcome.results, function(ci.data) {
        lapply(table.names, create_ci_level_tables, ci.data = ci.data)
    }
)

outcome.results.data <- enframe(outcome.results$point.estimates)
table.names <- strsplit(names(outcome.results$point.estimates), split = "\\|\\|\\.")
```

@@

## Create data report

```{r}
DataExplorer::create_report(data, report_title = "Data report", output_file = "data-report.pdf")
```
